---
title: "Pitch1"
output: ioslides_presentation
date: "2025-10-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

---
title: "Iris Species Predictor"
author: Akshay Ajit Parmar
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(randomForest)
```

## Slide 1: Title Slide

# Iris Species Predictor
### A Machine Learning Shiny App
<br>
**Your Name**
<br>
Data Science Specialization

---

## Slide 2: The Problem

### Botanical Identification Challenge

- Iris flowers come in multiple species
- Manual identification requires expertise
- Measurements can predict species accurately
- **Solution**: Accessible web app for quick predictions

```{r problem-plot, echo=FALSE, fig.height=4}
data(iris)
ggplot(iris, aes(x = Species, fill = Species)) + 
  geom_bar() +
  theme_minimal() +
  labs(title = "Iris Species Distribution", y = "Count")
```

---

## Slide 3: App Features

### Interactive Machine Learning

**Input Features:**
- Sepal length and width
- Petal length and width  
- Real-time slider controls

**Output:**
- Species prediction with confidence
- Probability breakdown
- Visual data positioning

```{r features-code, echo=TRUE, eval=FALSE}
# Example of the prediction model
model <- randomForest(Species ~ ., data = iris)
predict(model, new_data)
```

---

## Slide 4: Technical Implementation

### Under the Hood

**Technology Stack:**
- R Shiny framework
- Random Forest algorithm
- ggplot2 for visualization
- Deployed on Shinyapps.io

**Code Structure:**
```{r tech-structure, echo=TRUE, eval=FALSE}
iris-shiny-app/
â”œâ”€â”€ ui.R          # User interface
â”œâ”€â”€ server.R      # Server logic  
â””â”€â”€ README.md     # Documentation
```

**Model Performance:**
```{r model-performance, echo=FALSE}
set.seed(123)
train_idx <- sample(1:nrow(iris), 100)
train_data <- iris[train_idx, ]
test_data <- iris[-train_idx, ]
model <- randomForest(Species ~ ., data = train_data)
accuracy <- mean(predict(model, test_data) == test_data$Species)
cat("Test Accuracy:", round(accuracy * 100, 1), "%")
```

---

## Slide 5: Try It Yourself!

### Live Demo & Code

**Access the App:**
ðŸŒ https://akshay576.shinyapps.io/exploratory_p2/

**Source Code:**
ðŸ’» https://github.com/Akshay-parmar107/SHINYAPP/tree/main

**Key Benefits:**
- No botanical expertise required
- Instant predictions
- Educational visualization
- Open source code

<br>

**Thank You! Questions?**
