---
title: "Pitch in slidify"
output: slidy_presentation
date: "2025-10-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

---
title: "Iris Species Predictor"
author: Akshay Ajit Parmar
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(ggplot2)
library(randomForest)
```

## Slide 1: Title Slide

# Iris Species Predictor
### A Machine Learning Shiny App
<br>
**Your Name**
<br>
Data Science Specialization

---

## Slide 2: The Problem

### Botanical Identification Challenge

- Iris flowers come in multiple species
- Manual identification requires expertise
- Measurements can predict species accurately
- **Solution**: Accessible web app for quick predictions

```{r problem-plot, echo=FALSE, fig.height=4}
data(iris)
ggplot(iris, aes(x = Species, fill = Species)) + 
  geom_bar() +
  theme_minimal() +
  labs(title = "Iris Species Distribution", y = "Count")
```